ShrinkNets

### 2018-01-06 paper/paper.tex
Move legend and fix compilation
Attempt to fix some of the comments

\documentclass[sigconf]{acmart}
\sloppy
\usepackage{graphicx}
\usepackage{color}
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers
\makeatletter
\renewcommand\@formatdoi[1]{\ignorespaces}
\makeatother
\settopmatter{printacmref=false}

@@

\textbf{Filter Layers: } Filter layers have weights in the range $[0,+\infty]$ and are placed after
linear and convolutional layers.
%\gl{This is how I
%  used it but with the new implementation we can be more creative and put them
%  anywhere, should we say "usually placed" insdead ?}. 
The \textit{Filter Layer} takes an input of size $\left(B \times C \times D_1
\times \dots \times D_n\right)$, where $B$ is the batch size, $C$ the number of
features (or channels, in the case of convolutional layers), and $D$ any additional dimension. This structure makes
it compatible with fully connected layers with $n=0$ or convolutional layers
with $n=2$. Their crucial property is a parameter $\theta \in \mathbb{R}^C$,
defined as follows:
\vspace{-1em}
\begin{equation} Filter(I;\theta) = I \circ \max(0, \theta) \end{equation}
Where $\circ$ is the 
%Hadamard product (
pointwise multiplication,
%\gl{Should we
%  keep only one of them to be more concise ?}), 
and $\theta$ is expanded in all
dimensions except the second one \srm{why not the second one? what is the second one?  C?} to match the input size. It is easy to see
that if for any $k$, if $\theta_k \leq 0$, the $k^{\text{th}}$ feature/channel
will forever be $0$. When this happens, we say the Filter layer deactivates the
neuron. \srm{Not easy to see this because you haven't told me that theta only decays over time?} These disabled neurons/channels can be removed from the network without
changing its output. Before explaining how that is achieved, we 
% (we describe how we perform this removal below). We 
explain
next how the weights of the Filter Layer are adjusted during training. \srm{How are filter weights initialized?}

@@

%\subsection{The training procedure}
\textbf{Training Procedure: } Once Filter layers are placed in a network, 
%To train networks we need start with a substantially oversized network, then we
%insert \textit{Filter Layers}  (usually after every linear or convolutional
%layer except the last one) and we sample their weight from the
%$\text{Uniform}(0, 1)$ distribution. 
we could train the network directly using our standard loss function, and we could achieve performance equivalent to a normal neural
network. However, our goal is to find the smallest network with reasonable
performance. We achieve that by introducing sparsity in the parameters of the
\textit{Filter Layers}, thus forcing the deactivation of neurons \srm{by decaying the value of theta}
%. Indeed, having a negative component in the $\theta$
%parameter of the filter layer permamently disable its associated feature
%\gl{Maybe redundant ? we talked about that in the previous paragraph} . 
To obtain this sparsity, we simply redefine the loss function:
\vspace{-.5em}
\begin{equation}
  L'(x,y;\theta) = L(x, y) + \lambda|\theta|
\end{equation}

The additional term $\lambda|\theta|$ introduces sparsity (see Lasso
loss~\cite{Tibshirani1996}). \srm{Say lambda is in [0,1]?}
%This choice comes from the Lasso loss ~\cite{Tibshirani1996} and we use it for
%the same reason: it introduces sparsity. 
The $\lambda$ parameter adjusts how aggressively the network deactivates neurons,
with larger values indicating more aggressive deactivation. \srm{Give some intuitive statement about how this loss function causes theta to decay in irrelevant neurons, while preserving the value of important neurons.}
%The bigger the $\lambda$ the more
%entries in $\theta$ are set to zero, and 
Because the entries in $\theta$ with a value of $0$
correspond to dead neurons, $\lambda$ effectively controls the number of
neurons/channels in the entire network.  
Next, we explain how to implement
ShrinkNets efficiently.

\textbf{Dynamic Network Resizing}
It is possible to reduce the overhead of the training process by removing
neurons as soon as they become deactivated by $\theta$ going to 0.
%If
%disabled neurons are not quickly removed, the overhead might cause the training
%process to be significantly slower than classic neural networks. 
To do this, we implemented a \emph{neural garbage collection} mechanism which
prunes deactivated neurons on-the-fly,  reducing the processing time
and memory overhead. To support this feature, it is crucial to understand the
information flow between neurons and layers in the neural network. We achieve
this by representing such information flow as a graph, in which edges indicate
what action each node, i.e., neuron, must take. 
\srm{I can't really understand what this means -- need to add a bit more detail.}

@@

\ra{stopped here}

\begin{figure}
\vspace{-.2in}
\begin{center}
\includegraphics[width=0.9\columnwidth]{convergence}
\vspace{-.2in}
\caption{Evolution of the number of hidden units and loss over time on the \texttt{MNIST} dataset for different $\lambda$ values \label{convergence_plot}}
\srm{Move legend inside top of figure, to save space.}
\vspace{-.2in}
\end{center}
\end{figure}

\subsection{Does ShrinkNet find good networks?}

@@

The results in the figure show that ShrinkNets finds better networks with fewer
training iterations than the other methods, because it achieves higher median 
and less variable accuracies. Despite the simple nature of this experiment, we
believe that the results generalize to more complex search methods.
\srm{Note something about
how we expect this to bear out even with methods other than random search?}

@@

\begin{figure}
\vspace{-.2in}
\begin{center}
  \includegraphics[width=0.9\columnwidth]{hyper_opt}
  \vspace{-.2in}
\caption{Distributions of testing accuracy for different training methods, datasets and architectures using random search\label{hyper_opt_res}}
\vspace{-.2in}
\end{center}
\end{figure}

@@

There are many methods in the literature that aim to simplify network
structure. Most of them focuses on removing connections (eg: ~\cite{Cun},
~\cite{Han2015}).  \ra{not sure the following is relevant. Instead, just
contrast with the approach in this paper} However, most hardware (GPU's, TPUS ~\cite{Jouppi2017},
TensorCores) do not really leverage sparsity in the connections efficiently (as
explained in ~\cite{Han2016}). On the other side, ShrinkNets and some others
~\cite{Scardapane2017} and ~\cite{Philipp} try to remove entire neurons instead
of connections. This is very useful because it reduces the size of the matrices,
producing speed-up on every device. ShrinkNets improves on
~\cite{Scardapane2017} because it removes neurons during training, speeding up
the rest of the process. Further it outperforms~\cite{Philipp} on convergence
speed and because it does not need to change the optimizer. To the best of our
knowledge this is also the first work that tries to learn the number of channels
in a convolutional neural network.

>>>>

\documentclass[sigconf]{acmart}
\sloppy
\usepackage{graphicx}
\usepackage{color}
\settopmatter{printacmref=false} % Removes citation information below abstract
\renewcommand\footnotetextcopyrightpermission[1]{} % removes footnote with conference information in first column
\pagestyle{plain} % removes running headers
\makeatletter
\makeatother
\settopmatter{printacmref=false}

@@

\textbf{Filter Layers: } Filter layers have weights in the range $[0,+\infty]$ and are placed after
linear and convolutional layers.
%\gl{This is how I
%  used it but with the new implementation we can be more creative and put them
%  anywhere, should we say "usually placed" insdead ?}. 
The \textit{Filter Layer} takes an input of size $\left(B \times C \times D_1
  \times \dots \times D_n\right)$, where $B$ is the batch size, $C$ the number
of features (or channels, in the case of convolutional layers), and $D$ any
additional dimension. This structure makes it compatible with fully connected
layers with $n=0$ or convolutional layers with $n=2$. Their crucial property is
a parameter $\theta \in \mathbb{R}^C$, defined as follows: \vspace{-1em}
\begin{equation} Filter(I;\theta) = I \circ \max(0, \theta) \end{equation}
Where $\circ$ is the pointwise multiplication, and $\theta$ is expanded in all
dimensions to match the input size (except the second one since they are equal by definition). It is easy to see that if for any
$k$, if $\theta_k \leq 0$, the $k^{\text{th}}$ feature/channel will forever be
$0$. When this happens, we say the Filter layer deactivates the neuron.
\srm{Not easy to see this because you haven't told me that theta only decays
  over time?} \gl{The decay is only caused by the loss, and actually it does not depends on how it became zero, if it is zero for any reason, multiplying by zero will nullfy any value and cancel any gradient going through the layer} These disabled neurons/channels can be removed from the network
without changing its output. Before explaining how that is achieved, we explain
next how the weights of the Filter Layer are initialized and adjusted during training.

@@

%\subsection{The training procedure}
\textbf{Training Procedure: } Once Filter layers are placed in a network and initialized (sampled from the Uniform$[0, 1]$ distribution),
%To train networks we need start with a substantially oversized network, then we
%insert \textit{Filter Layers}  (usually after every linear or convolutional
%layer except the last one) and we sample their weight from the
%$\text{Uniform}(0, 1)$ distribution. 
we could train the network directly using our standard loss function, and we could achieve performance equivalent to a normal neural
network. However, our goal is to find the smallest network with reasonable
performance. We achieve that by introducing sparsity in the parameters of the
\textit{Filter Layers}, thus forcing the deactivation of neurons \srm{by decaying the value of theta} \gl{$\theta$ only decays (and only for some features), only because of the loss function that we have not defined yet at this moment in the paper}
%. Indeed, having a negative component in the $\theta$
%parameter of the filter layer permamently disable its associated feature
%\gl{Maybe redundant ? we talked about that in the previous paragraph} . 
To obtain this sparsity, we simply redefine the loss function:
\vspace{-.5em}
\begin{equation}
  L'(x,y;\theta) = L(x, y) + \lambda|\theta|
\end{equation}

The additional term $\lambda|\theta|$ introduces sparsity (see Lasso
loss~\cite{Tibshirani1996}). 
% The $\lambda$ parameter, that can take any
% positive value, adjusts how aggressively the network deactivates neurons, with
% larger values indicating more aggressive deactivation.
Indeed, the second component of the loss, because it increases the gradient in
respect with $\theta$, pushes its value towards zero. Neurons with little
impact on the original loss (gradient lower than $\lambda$), will not be able
to compete against this attraction towards zero. Because the entries in
$\theta$ with a value of $0$ correspond to dead neurons, $\lambda$ effectively
controls the number of neurons/channels in the entire network.  Next, we
explain how to implement ShrinkNets efficiently.

\textbf{Dynamic Network Resizing}
It is possible to reduce the overhead of the training process by removing
neurons as soon as they become deactivated by $\theta$ going to 0.
%If
%disabled neurons are not quickly removed, the overhead might cause the training
%process to be significantly slower than classic neural networks. 
To do this, we implemented a \emph{neural garbage collection} mechanism which
prunes deactivated neurons on-the-fly,  reducing the processing time
and memory overhead. To support this feature, it is crucial to understand the
information flow between neurons and layers in the neural network. We achieve
this by representing such information flow as a graph. Vertices represent layers,
and edges are event-hubs responsible for propagating information about disabled
neurons to the relevant layers.

@@

\begin{figure}
\vspace{-.2in}
\begin{center}
\includegraphics[width=\columnwidth]{convergence}
\vspace{-.2in}
\caption{Evolution of the number of hidden units and loss over time on the \texttt{MNIST} dataset for different $\lambda$ values \label{convergence_plot}}
\vspace{-.2in}
\end{center}
\end{figure}
\subsection{Does ShrinkNet find good networks?}

@@

The results in the figure show that ShrinkNets finds better networks with fewer
training iterations than the other methods, because it achieves higher median 
and less variable accuracies. Despite the simple nature of this experiment, we
believe that the results generalize to more complex search methods.

@@

\begin{figure}
\vspace{-.2in}
\begin{center}
  \includegraphics[width=\columnwidth]{hyper_opt}
  \vspace{-.2in}
\caption{Distributions of testing accuracy for different training methods, datasets and architectures using random search\label{hyper_opt_res}}
\vspace{-.2in}
\end{center}
\end{figure}

@@

There are many methods in the literature that aim to simplify network
structure. Most of them focuses on removing connections (eg: ~\cite{Cun},
~\cite{Han2015}). On the other side, ShrinkNets and some others
~\cite{Scardapane2017} and ~\cite{Philipp} try to remove entire neurons instead
of connections. This is very useful because it reduces the size of the matrices,
producing speed-up on every device. ShrinkNets improves on
~\cite{Scardapane2017} because it removes neurons during training, speeding up
the rest of the process. Further it outperforms~\cite{Philipp} on convergence
speed and because it does not need to change the optimizer. To the best of our
knowledge this is also the first work that tries to learn the number of channels
in a convolutional neural network.
